### 2021-04-15 input/abstract.tex

\begin{abstract}
%% Context and problem
  Edge infrastructures have been proposed as an alternative to Cloud
  Computing to provide computing and storage capabilities closer to
  the locations where data is generated/consumed, with the objectives
  of reducing the latency and the volume of data passing through the
  network. A few systems have been proposed to store data in those
  infrastructures. Unfortunately, locating the closest copy of a
  specific content in these systems requires to keep up-to-date an index
  of all replicas and their respective locations. While flooding
  approaches will not enable the maintenance of such an index for each
  node in large systems, relying on a dedicated service contradicts
  with the properties of Edge infrastructures in terms of locality and
  robustness (locating sources may effectively take more time than
  actually downloading contents).

%%% Our proposal
  In this paper, we introduce \NAME, an efficient broadcast protocol
  that relies on dynamic logical partitioning of the
  infrastructure. \NAME only floods the relevant nodes (\ie the ones
  that should be informed of a the creation of a closest copy),
  enabling to keep up-to-date an index for each node eventually.  In
  addition to demonstrating formally the correctness of our protocol \TODO{Is it true?},
  we discuss several evaluatons performed by simulations and show
  \TODO{blabla}.  While \NAME tackles our location problem, it can be
  used as a building block to design new advanced services such as
  \TODO{blabla}.

\end{abstract}

%\TODO{source automatically create
%    partitions.} \NAME uses epidemic dissemination (\TODO{scoped
%    flooding}). \TODO{costs of operations.} When the system becomes
%  quiescent, every process eventually converges to its closest
%  partition, then \NAME incurs no overhead. \TODO{Proof, simulation,
%+    testbed?}

>>>>

\begin{abstract}
  %% Context and problem
  Although the holy grail to store and manipulate data in Edge
  infrastructures is yet to be found, state-of-the-art approaches
  demonstrated the relevance of replication strategies that bring
  contents closer to consumers: The latter enjoy better response time
  while the volume of data passing through the network decreases
  overall.
  %% Although, there is no major solution to store and manipulate data in
  %% Edge infrastructures yet, existing proposals demonstrated the
  %% relevance of appropriate replication strategies to bring contents
  %% closer to consumers, reducing the impact of the latency as well as
  %% the volume of data passing through the network overall.  
  Unfortunately, locating the closest replica of a specific content
  requires indexing \emph{every live} replica along with its
  \emph{location}.
  %
  %Current proposals built on a centralized service face scalability
  %issues, single point of failure, as well as latency penalities where
  %locating replicas may effectively take more time than actually
  %downloading contents. Instead, data consumer \processes must
  %maintain an up-to-date index themselves. Unfortunately, maintaining
  %an index of all live replicas at every \process would prove overly
  %costly in terms of memory and generated traffic, especially in large
  %scale dynamic systems where \processes create and destroy replicas
  %at any time.
  % 
  Relying on remote services contradicts with the properties of Edge
  infrastructures as locating replicas may effectively take more time
  than actually downloading contents.  At the opposite, maintaining
  such an index at every \process would prove overly costly in terms
  of memory and traffic, especially since \processes can create and
  destroy replicas at any time.

  %%% Our proposal
  \noindent In this paper, we abstract content indexing as distributed
  partitioning: every \process only indexes its closest replica, and
  connected \processes with similar index compose a partition. Our
  decentralized implementation \NAME
  \begin{inparaenum}[(i)]
  \item is efficient, for it uses partitions to lock down the traffic
    generated by its operations, yet it
  \item guarantees that every \process eventually acknowledges its
    partition despite concurrent operations.
  \end{inparaenum}
  %% When a \node replicates a content, it notifies all \nodes (new
  %% members of its partition) that are closer from it than any other
  %% replica; When a \node destroys a replica, it notifies members of
  %% its partition to switch to another closer partition. \NAME
  %% guarantees that eventually, every \process knows its best
  %% partition, hence its closest replica, despite concurrent
  %% operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and termination time,
  especially in dynamic Edge infrastructures. As such, \NAME could
  constitute the building block of new advanced services such as
  decentralized recommendation systems.
\end{abstract}
